\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

Thirdly, the calculation of $max$ and $sum$ can be accomplished in one loop by adjusting $sum$ whenever a higher $max$ is found:
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $max_a$ is the original maximum value, $max_b$ is the new, higher maximum value, ie. $max_b > max_a$, and $\Delta = max_a - max_b$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

These changes do not reduce the asymptotic runtime of our algorithm, which remains at $\mathcal{O}(|p|)$, but it does bring the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.

@@

>>>>

Thirdly, the calculation of $max$ and $sum$ can be accomplished in one loop by adjusting $sum$ whenever a higher $max$ is found during the looping:
\begin{eqnarray*}
sum & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_b}} \\
    & = & e^{x_t - max_b} + \sum_{i=0...t-1}{e^{x_i - max_a + \Delta}}  \\
    & = & e^{x_t - max_b} + e^{\Delta} \times \sum_{i=0...t-1}{e^{x_i - max_a}} 
\end{eqnarray*}
where $max_a$ is the original maximum value, $max_b$ is the new, higher maximum value, ie. $max_b > max_a$, and $\Delta = max_a - max_b$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

%These changes do not reduce the asymptotic runtime of our algorithm, which remains at $\mathcal{O}(|p|)$, but it does bring the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.

@@

Using batching can increase the translation speed by over 20 times in Amun and shows little degradation with larger batch sizes, Figure~\ref{fig:batch-size}. This contrast with using the Marian, which uses a simpler batching algorithm, where the speedup is approximately 16 times and inference speed slows down when the batch size is above 1000.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batch size during decoding}
\label{fig:batch-size}
\end{figure}
